---
params:
  age_lower: !r NA_real_
  age_upper: !r NA_real_
  authorship_1_chr: ''
  authorship_2_chr: ''
  data_pckg_chr: springtides
  disorder_chr: !r NA_character_
  format_chr: PDF
  gdist_dbl: !r NA_real_
  gdist_ttime_chr: !r NA_character_
  input_ls_path_chr: !r NA_character_
  meso2_bound_yr: !r NA_real_
  meso2_chr: !r NA_character_
  meso2_name_chr: !r NA_character_
  meso2_type_chr: !r NA_character_
  micro_chr_vec: !r NA_character_
  model_end_date: !r Sys.Date()
  model_start_date: !r springtides::aus_pa_r4@temporal_min
  n_its_int: !r NA_real_
  output_params_ls_path_chr: !r NA_character_
  pa_r4_chr: aus_pa_r4
  pa_type_chr: !r NA_character_
  pdf_output_lgl: !r T
  r_data_dir_chr: data
  rendered_by_shiny_lgl: !r F
  sim_data_r4_path_chr: !r NA_character_
  sim_results_ls_path_chr: !r NA_character_
  stat_chr: Prevalence - Annual
  title_chr: "Scenario Anaysis: Impact on mental disorder prevalence due to COVID-19 Systemic Shock"
  ttime_dbl: !r NA_real_
  uncertainty_1_int: 0.025
  uncertainty_2_int: 0.975
  user_name_chr: !r NA_character_
title: "`r params$title_chr`"
author:
  - "`r params$authorship_1_chr`"
  - "`r params$authorship_2_chr`"
date: "`r format.Date(Sys.Date(),'%B %d, %Y')`"
output:
  pdf_document:
    fig_caption: yes
  word_document: default
  html_document:
    df_print: paged
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

```{r echo=F, warning=F, message=F, eval=T}
library(magrittr)
library(kableExtra)
library(springtides)
library(ready4sim)
r_data_path_chr <- "C:/Users/mahamilton/Desktop/Readyforwhatsnext/Data/R_Format"
project_data_path_chr <- r_data_path_chr %>% stringr::str_replace("R_Format","Project/COVID19")
res_path_chr <- paste0(project_data_path_chr,
                                    "/WA_04_84")
bc_res_ls <- readRDS(paste0(res_path_chr,
                            "/sim_res_bc.RDS"))
sk_res_ls <- readRDS(paste0(res_path_chr,
                            "/sim_res_shock_only.RDS"))
# pa_x_params_ls_path_chr <- paste0(project_data_path_chr,
#                                     "/",
#                                     pa_dir_chr,
#                                     "/output_params_ls.rds")
output_params_ls <- readRDS(paste0(res_path_chr,
                            "/output_params_ls.RDS"))
# if(is.na(params$output_params_ls_path_chr)){
#   output_params_ls <- springtides::make_output_params_ls(input_params_ls = params)
# }else{
#   output_params_ls <- readRDS(params$output_params_ls_path_chr)
# }

```

```{r include=FALSE}
# bc_res_ls <- readRDS(paste0(project_data_path_chr,"/sim_res_bc.RDS"))

# sim_data_r4 <- readRDS(paste0(project_data_path_chr,"/sim_data_r4.RDS"))
# sim_results_ls <- bc_res_ls
input_params_ls <- params
input_ls <- output_params_ls$input_ls #readRDS(paste0(project_data_path_chr,"/input_ls.RDS"))
# #bc_res_ls[[1]][[2]] %>% nrow()
# saveRDS(input_ls,
#         paste0(project_data_path_chr,
#                                              "/",
#                                     pa_dir_chr,"/input_ls.RDS"))
# saveRDS(output_params_ls$sim_data_r4,paste0(project_data_path_chr,
#                                                 "/",
#                                     pa_dir_chr,
#                                     "/sim_data_r4.RDS"))
```

```{r include=FALSE}
# input_params_ls$sim_results_ls_path_chr <- paste0(project_data_path_chr,
#                                                    "/",
#                                     pa_dir_chr,
#                                     "/sim_res_bc.RDS")
# input_params_ls$sim_data_r4_path_chr <- paste0(project_data_path_chr,
#                                                 "/",
#                                     pa_dir_chr,
#                                     "/sim_data_r4.RDS")
# input_params_ls$input_ls_path_chr <- paste0(project_data_path_chr,
#                                              "/",
#                                     pa_dir_chr,"/input_ls.RDS")
input_params_ls$age_lower <- input_ls$age_lower
input_params_ls$age_upper <- input_ls$age_upper
input_params_ls$meso2_name_chr <- input_ls$pa_r4@features
input_params_ls$disorder_chr <- input_ls$disorder
```

```{r}
diff_tb <-purrr::map2_dfr(sk_res_ls,
            bc_res_ls,
           ~ {
             abc <- .x[[1]] %>% dplyr::select_if(is.numeric) 
  def <- .y[[1]] %>% dplyr::select_if(is.numeric)
abc-def
})

```


```{r echo=F, warning=F, message=F, eval=T}
make_original_tb <- function(res_ls){
vars_chr_vec <- res_ls[[1]]$summary_tb %>% names()
prev_vars_chr_vec <- vars_chr_vec[vars_chr_vec %>% endsWith("prev_any_common_mental_disorder_p_tl")] 
tx_pop_var_chr <- vars_chr_vec[vars_chr_vec %>% endsWith("_p_tl") & vars_chr_vec %>% startsWith("tx_") & !vars_chr_vec %in% prev_vars_chr_vec]
res_ls %>%
  purrr::map_dfr(~tibble::tibble(Tx = .x$summary_tb %>% dplyr::pull(prev_vars_chr_vec[prev_vars_chr_vec %>% startsWith("tx")]),
                                 T0 = .x$summary_tb %>% dplyr::pull(prev_vars_chr_vec[prev_vars_chr_vec %>% startsWith("t0")]),
                                 Tx_pop = .x$summary_tb %>% dplyr::pull(tx_pop_var_chr))) %>%
  dplyr::summarise_all(mean) %>%
  t()
}
make_comparisons_tb <- function(bc_res_ls,
                                shock_res_ls){
vars_chr_vec <- bc_res_ls[[1]]$summary_tb %>% names()
prev_var_chr <- vars_chr_vec[vars_chr_vec %>% endsWith("prev_any_common_mental_disorder_p_tl") &
                               vars_chr_vec %>% startsWith("tx_")] 
  comparisons_tb <- purrr::map2_dfr(bc_res_ls,
                                shock_res_ls,
                                ~ tibble::tibble(`Base case` = .x$summary_tb %>% dplyr::pull(prev_var_chr),
`Base case plus shock` = .y$summary_tb %>% dplyr::pull(prev_var_chr)#,
# `Base case plus background risk` = .x$SYD_BC_tx_prev_any_common_mental_disorder_p_tl %>% sum(),
# `Base case plus shock plus background risk` = .x$SYD_BC_TX_PREV_ANY_COMMON_MENTAL_DISORDER_P_TL_S1_EXCESS %>% sum(),
)
                                    ) %>%
  dplyr::summarise_all(mean) %>%
  t()
colnames(comparisons_tb) <- c("Prevalent population")
comparisons_tb  %>% as.data.frame() %>% tibble::rownames_to_column() %>%
  dplyr::rename(Scenario = rowname)
}
update_comparisons_tb <- function(comparisons_tb,
                                  original_tb){
 comparisons_tb <- comparisons_tb %>%
  #tibble::as_tibble() %>%
  dplyr::mutate(`Proportion of population` = .$`Prevalent population`/original_tb["Tx_pop",1]) %>%
  dplyr::mutate(`Change from Springtides Baseline` = .$`Prevalent population`-original_tb["T0",1]) %>%
  dplyr::mutate(`Annual QALY Difference (Springtides_Baseline)` = 121/365.25*0.21 * .$`Change from Springtides Baseline`) %>%
  dplyr::mutate(`Implied health financing requriement` = .$`Annual QALY Difference (Springtides_Baseline)`*28033*1.166) 
}
add_health_utility_tb <- function(diff_tb,
                                  shock_tb,
                                  base_tb){
  prev_cols_chr <- names(shock_tb)[names(shock_tb) %>% startsWith("delta") & names(shock_tb) %>% stringr::str_sub(start = -14)=="_disorder_p_tl"]
  pop_cols_chr <- names(shock_tb)[(names(base_tb) %>% startsWith("ti")|names(base_tb) %>% startsWith("tx")) & names(shock_tb) %>% stringr::str_sub(start = -5)=="_p_tl" & !names(shock_tb) %>% stringr::str_sub(start = -14)=="_disorder_p_tl"] 
excess_prev_tb <- diff_tb %>% dplyr::select(tidyselect::all_of(prev_cols_chr))
excess_hu_burden_tb <- excess_prev_tb  %>% dplyr::summarise_all(mean) * 121/365.25*0.21
fin_req_tb <- excess_hu_burden_tb *28033*1.166
fin_mat <- t(fin_req_tb)
tot_fin_dbl <- fin_mat %>% sum()  
annual_fin_req <- rep(tot_fin_dbl/nrow(fin_mat),nrow(fin_mat))
annual_fin_req_s1 <- annual_fin_req * 0.33
annual_fin_req_s2 <- annual_fin_req * 0.66
annual_fin_req_s3 <- annual_fin_req * 1
excess_hu_burden_tb <- excess_prev_tb * 121/365.25*0.21
annual_hu_return_s1 <- c(0,annual_fin_req_s1[2:length(annual_fin_req_s1)])/(28033*1.166)
sc_1_hu_burden_tb <- excess_hu_burden_tb-annual_hu_return_s1
annual_hu_return_s2 <- c(0,annual_fin_req_s2[2:length(annual_fin_req_s2)])/(28033*1.166)
sc_2_hu_burden_tb <- excess_hu_burden_tb-annual_hu_return_s2
annual_hu_return_s3 <- c(0,annual_fin_req_s3[2:length(annual_fin_req_s3)])/(28033*1.166)
sc_3_hu_burden_tb <- excess_hu_burden_tb-annual_hu_return_s3
sc_3_hu_burden_tb <- excess_hu_burden_tb-annual_hu_return_s3
list(excess_hu_burden_tb = excess_hu_burden_tb,
     fin_req_tb = fin_req_tb,
     tot_fin_dbl = tot_fin_dbl,
     sc_ls = list(one_thirds = list(annual_fin_req_s1 = annual_fin_req_s1,
                                   annual_hu_return_s1 = annual_hu_return_s1,
                                   sc_1_hu_burden_tb = sc_1_hu_burden_tb),
                  two_thirds = list(annual_fin_req_s2 = annual_fin_req_s2,
                                   annual_hu_return_s2 = annual_hu_return_s2,
                                   sc_2_hu_burden_tb = sc_2_hu_burden_tb),
                  complete = list(annual_fin_req_s3 = annual_fin_req_s3,
                                   annual_hu_return_s3 = annual_hu_return_s3,
                                   sc_3_hu_burden_tb = sc_3_hu_burden_tb)))
}
```

```{r echo=F, warning=F, message=F, eval=T}
original_tb <- make_original_tb(bc_res_ls)
comparisons_tb <- make_comparisons_tb(bc_res_ls, shock_res_ls = sk_res_ls) %>%
update_comparisons_tb(original_tb = original_tb)
```

```{r echo=F, warning=F, message=F, eval=T}
comparisons_tb <- comparisons_tb %>%
  dplyr::slice(1:2) %>%
  dplyr::rename(`Prevalent population counts in 2024/2025`=`Prevalent population`,
                `Prevalent population proportion in 2024/25`=`Proportion of population`,
                `Change in prevalent population from 2020 Base case` = `Change from Springtides Baseline`,
               `Change in annual QALYs from 2020 Base Case` = `Annual QALY Difference (Springtides_Baseline)`,
               `Health system financing requirement to offset change` = `Implied health financing requriement`) %>%
  t() %>% 
  as.data.frame() %>% tibble::rownames_to_column()  

  names(comparisons_tb ) <- c("Statistic", "Base case", "COVID shock")
 comparisons_tb <- comparisons_tb [-1,] %>%
    tibble::as_tibble() %>%
    dplyr::mutate_at(.vars = c("Base case", "COVID shock"), .funs = as.character) %>%
    dplyr::mutate_at(.vars = c("Base case", "COVID shock"), .funs = as.numeric) 


    #dplyr::bind_rows(tibble::tibble(Statistic= ))
#%>% janitor::row_to_names(1)
  
```


```{r echo=F, warning=F, message=F, eval=T}
 comparisons_tb <- dplyr::bind_rows(comparisons_tb[1:3,],
                 tibble::tibble(Statistic = "COVID-19 excess prevalent counts in 2024/25",
                                `Base case` = c(NA_real_),
                                `COVID shock` = comparisons_tb[[1,3]]-comparisons_tb[[1,2]] 
                 ))

# write.csv(comparisons_tb,
#           paste0(project_data_path_chr,"/comparisons_tb.csv"))
  
```

```{r echo=F, warning=F, message=F, eval=T}
comparisons_tb <- dplyr::bind_rows(comparisons_tb,
                 tibble::tibble(Statistic = "Health utility impact (in QALYs) of excess prevalence in 2024/25",
                                `Base case` = c(NA_real_),
                                `COVID shock` = comparisons_tb[[4,3]]* 121/365.25*0.21
                 ))

```

```{r echo=F, warning=F, message=F, eval=T}
parts_1_3 <- comparisons_tb %>%
  dplyr::mutate_at(.vars = c("Base case", "COVID shock"),
                   ~ purrr::map_chr(.,
                                          ~format(.x,decimal.mark=".",big.mark=",", small.interval=3)))
part_2 <- comparisons_tb %>%
  dplyr::filter(Statistic == "Prevalent population proportion in 2024/25") %>%
    dplyr::mutate_at(.vars = c("Base case", "COVID shock"),
                   ~ purrr::map_chr(.,
                                          ~scales::percent(.x)))
counterfactual_tb <-dplyr::bind_rows(parts_1_3[1,],
                 part_2,
                 parts_1_3[3:5,])
```


```{r echo=F, warning=F, message=F, eval=T}
financing_req_chr <-paste0("$",(comparisons_tb[[5,3]]*28033*1.166) %>% format(decimal.mark=".",big.mark=",",small.mark=".", small.interval=3))
```

```{r}
tibble::add_case(counterfactual_tb,
                 Statistic = "Health financing requirement to offset QALY loss (A$)",
                 `COVID shock` = financing_req_chr)
```

Not for citation or public dissemination. 

# Introduction
This document explores the potential impact of the significant social and economic disruption arising from COVID-19 on `r output_params_ls$tfd_stat_chr %>% tolower()` amongst `r output_params_ls$age_lower` to `r output_params_ls$age_upper` year olds resident in `r output_params_ls$meso2_name_chr` between  `r output_params_ls$tfd_start_date_chr` and `r output_params_ls$tfd_end_date_chr`.

# Modelling Steps and Outputs

## Demographic Projections
We first predicted the population of `r output_params_ls$age_lower` to `r output_params_ls$age_upper` year olds resident in `r output_params_ls$meso2_name_chr`. These predictions do not account for any potential COVID-19 disruptions to migration or mortality.

### `r paste0("Predicted Change in Resident Population Between ", output_params_ls$tfd_start_date_chr, " and ",output_params_ls$tfd_end_date_chr)`

```{r echo=F, warning=F}
output_params_ls$output_tables_ls[[9]]
```


```{r echo=F, warning=F, fig.cap=output_params_ls$output_plots_titles_ls$Figure_9}
output_params_ls$output_plots_ls$Figure_9
```

\pagebreak

## `r output_params_ls$tfd_stat_chr` Base Case
We next applied age and sex prevalence rates estimated from the most recent Australian surveys to predicted `r output_params_ls$tfd_stat_chr %>% tolower()` amongst `r output_params_ls$age_lower` to `r output_params_ls$age_upper` year olds resident in `r output_params_ls$meso2_name_chr`. These rates neither account for any potential change in the background prevalence of mental disorder since these surveys were undertaken, not for the potential impacts of the systemic shock arising from COVID-19.

```{r echo=F, warning=F}
output_params_ls$output_tables_ls[[12]]
```


```{r echo=F, warning=F, fig.cap=output_params_ls$output_plots_titles_ls$Figure_12}
output_params_ls$output_plots_ls$Figure_12
```

\pagebreak

```{r echo=F, warning=F}
output_params_ls$output_tables_ls[[15]]
```


```{r echo=F, warning=F, fig.cap=output_params_ls$output_plots_titles_ls$Figure_15}
output_params_ls$output_plots_ls$Figure_15
```

\pagebreak

### `r paste0("Predicted Change in "," ",output_params_ls$tfd_stat_chr," Between ", output_params_ls$tfd_start_date_chr, " and ",output_params_ls$tfd_end_date_chr)`

```{r echo=F, warning=F}
output_params_ls$output_tables_ls[[18]]
```


```{r echo=F, warning=F, fig.cap=output_params_ls$output_plots_titles_ls$Figure_18}
output_params_ls$output_plots_ls$Figure_18
```

\pagebreak

## COVID-19 Counterfactual
Finally, we modelled one counterfactual scenario - that of an increase in prevalence rates due to the COVID-19 systemic shock. This scenario did not explore any potential change in background prevalence between the conduct of national Australian epidemiological surveys that are the source of our base case prevalence rate data nor any demographic change (population size and composition) arising from the COVID-19 systemic shock.

```{r echo=F, warning=F}
counterfactual_tb

```

To explore the cost of mitigating the population health utility loss under this scenario, we multiplied the projected Quality Adjusted Life Years (QALYs) lost by an empirical estimate of the marginal productivity of Australian healthcare expenditure in dollars per QALY. The estimated healthcare financing requirement to completely offset the projected health loss due to the COVID-19 systemic shock modelled under this scenario is `r financing_req_chr`.



```{r echo=F, warning=F, message=F, eval=T}
# r_data_path_chr <- "C:/Users/mahamilton/Desktop/Readyforwhatsnext/Data/R_Format"
# project_data_path_chr <- r_data_path_chr %>% stringr::str_replace("R_Format","Project/COVID19")
# path_to_K10_data_chr <- paste0(project_data_path_chr,"/Copy of Psychological Distress - North Coast outputs.xlsx")
# start_date_dtm <- lubridate::ymd_hms("2011-01-01 00:00:00", 
#                                      tz = "Australia/Melbourne") 
# pa_dir_chr <- "WA_04_84"
# pa_x_params_ls_path_chr <- paste0(project_data_path_chr,
#                                     "/",
#                                     pa_dir_chr,
#                                     "/output_params_ls.rds")
# output_params_ls <- readRDS(pa_x_params_ls_path_chr)
```

```{r}
# bc<-input_params_ls$sim_results_ls_path_chr %>% readRDS()
# bc[[1]][[1]]$t0_20200506_p_tl

```

```{r include=FALSE}
# output_params_ls <- make_slim_out_ls(input_params_ls)
```

```{r include=FALSE}
# input_params_ls$sim_results_ls_path_chr <- paste0(project_data_path_chr,"/",
#                                     pa_dir_chr,"/sim_res_shock_only.RDS")
# shock_output_params_ls <- make_slim_out_ls(input_params_ls)
```


```{r echo=F, warning=F}
# if(output_params_ls$rendered_by_shiny_lgl)
#   shiny::setProgress(1, message = "Step five: Wrap up") 
# add_shock_RR_tb <- function(res_tb,
#                                 RR_tb,
#                                 starts_with_chr_vec){
#             res_tb %>%
#                dplyr::mutate_at(dplyr::vars(dplyr::starts_with(starts_with_chr_vec[1])), #t0_prev
#                                        .funs = list(s1_excess = ~ RR_tb %>%
#   dplyr::slice(1) %>% dplyr::pull(`Scenario 1_RR`)*.,
#                                                     s2_excess = ~ RR_tb %>%
#   dplyr::slice(1) %>% dplyr::pull(`Scenario 2_RR`) *.,
#                                                     s1_i1_excess = ~ RR_tb %>%
#   dplyr::slice(1) %>% dplyr::pull(`Scen. 1, int. 1_RR`) *.,
#                                                     s1_i2_excess = ~ RR_tb %>%
#   dplyr::slice(1) %>% dplyr::pull(`Scen. 1, int. 2_RR`) *.,
#                                                     s1_i3_excess = ~ RR_tb %>%
#   dplyr::slice(1) %>% dplyr::pull(`Scen. 1, int. 3_RR`) *.,
#                                                     s1_i4_excess = ~ RR_tb %>%
#   dplyr::slice(1) %>% dplyr::pull(`Scen. 1, int. 4_RR`) *.,
#                                                     s1_i5_excess = ~ RR_tb %>%
#   dplyr::slice(1) %>% dplyr::pull(`Scen. 1, int. 5_RR`) *.)
#                                 
#                                 ) %>%
#                dplyr::mutate_at(dplyr::vars(dplyr::starts_with(starts_with_chr_vec[2])), #tx_prev
#                                        .funs = list(s1_excess = ~ RR_tb %>%
#   dplyr::slice(2) %>% dplyr::pull(`Scenario 1_RR`)*.,
#                                                     s2_excess = ~ RR_tb %>%
#   dplyr::slice(2) %>% dplyr::pull(`Scenario 2_RR`) *.,
#                                                     s1_i1_excess = ~ RR_tb %>%
#   dplyr::slice(2) %>% dplyr::pull(`Scen. 1, int. 1_RR`) *.,
#                                                     s1_i2_excess = ~ RR_tb %>%
#   dplyr::slice(2) %>% dplyr::pull(`Scen. 1, int. 2_RR`) *.,
#                                                     s1_i3_excess = ~ RR_tb %>%
#   dplyr::slice(2) %>% dplyr::pull(`Scen. 1, int. 3_RR`) *.,
#                                                     s1_i4_excess = ~ RR_tb %>%
#   dplyr::slice(2) %>% dplyr::pull(`Scen. 1, int. 4_RR`) *.,
#                                                     s1_i5_excess = ~ RR_tb %>%
#   dplyr::slice(2) %>% dplyr::pull(`Scen. 1, int. 5_RR`) *.)
#                                 
#                ) %>% dplyr::rename_at(
#                                   dplyr::vars(ends_with("_excess")), function(x) { toupper(x) }
# )
#                                 }
# add_alt_model_RR_tb <- function(res_tb,
#                                   col_pfx_chr,
#                                   time_RR_chr,
#                                   new_pfx_chr = "SYD_BC_",
#                                   RR_lup){
#   all_names_chr_vec <- res_tb %>% names()
#   target_cols_chr_vec <- all_names_chr_vec[all_names_chr_vec %>% startsWith(col_pfx_chr)]#t0_prev
# 
#   sum_cols_chr_vec <- target_cols_chr_vec[endsWith(target_cols_chr_vec,
#                                                    "_tl")]
#   p_sum_col_chr_vec <- sum_cols_chr_vec[endsWith(sum_cols_chr_vec,
#                                                    "p_tl")]
#   fm_sum_cols_chr_vec <- sum_cols_chr_vec[sum_cols_chr_vec != p_sum_col_chr_vec] %>% sort()
#   target_cols_chr_vec <- target_cols_chr_vec[!target_cols_chr_vec %in% sum_cols_chr_vec]
#   target_age_chr_vec <- purrr::map_chr(target_cols_chr_vec,
#                                          ~ stringr::str_sub(.x,start=-2))  
#   res_tb <- purrr::reduce(1:(length(target_cols_chr_vec)),
#                          .init = res_tb,
#                   ~ {
#                     tb <- .x
#                     col_chr <- target_cols_chr_vec[.y]
#                     age_dbl <- target_age_chr_vec[.y]
#                     RR_dbl <- ready4utils::data_get(RR_lup,
#                                                     lookup_reference = age_dbl,
#                                                     lookup_variable = "age_dbl",
#                                                     target_variable = time_RR_chr,#"t0_RR"
#                                                     evaluate = F)
#                     dplyr::mutate(tb,
#                                   !!rlang::sym(paste0(new_pfx_chr,
#                                                       col_chr)) := purrr::map_dbl(tb %>% 
#                                                                                     dplyr::pull(col_chr),
#                                                                                   ~ ifelse(identical(.x,
#                                                                                                      numeric(0)),
#                                                                                                      NA_real_,
#                                                                                                      .x * RR_dbl)
#                                                                                                    
#                                                                                                    )) 
#     })
# add_sum_col_tb(res_tb = res_tb,
#                target_cols_chr_vec = target_cols_chr_vec,
#                new_pfx_chr = new_pfx_chr,
#                fm_sum_cols_chr_vec = fm_sum_cols_chr_vec,
#                p_sum_col_chr_vec = p_sum_col_chr_vec)
# 
# }
# add_sum_col_tb <- function(res_tb,
#                            target_cols_chr_vec,
#                            new_pfx_chr = "",
#                            fm_sum_cols_chr_vec,
#                            p_sum_col_chr_vec){
#     female_cols_chr_vec <- paste0(new_pfx_chr,
#                                 target_cols_chr_vec["f_"==target_cols_chr_vec %>% stringr::str_sub(start=-4,end=-3)])
#   male_cols_chr_vec <- paste0(new_pfx_chr,
#                               target_cols_chr_vec["f_"==target_cols_chr_vec %>% stringr::str_sub(start=-4,end=-3)])
#   fm_sum_cols_chr_vec <- paste0(new_pfx_chr,fm_sum_cols_chr_vec)
#   purrr::reduce(list(female = list(fm_sum_cols_chr_vec[1],
#                                      female_cols_chr_vec),
#                        male = list(fm_sum_cols_chr_vec[2],
#                                    male_cols_chr_vec)),
#                        .init = res_tb,
#                     ~ .x %>%
#     dplyr::mutate(!!rlang::sym(.y[[1]][1]) := dplyr::select(., .y[[2]]) %>% rowSums(na.rm = TRUE)))  %>%
#     dplyr::mutate(!!rlang::sym(paste0(new_pfx_chr,p_sum_col_chr_vec)) := dplyr::select(.,fm_sum_cols_chr_vec) %>% rowSums(na.rm = TRUE))
#                            }
# import_model_output_tb <- function(path_to_K10_data_chr,
#                                    range_ls,
#                                    start_date_dtm){
#   purrr::map(range_ls,
#              ~ {
#                tb <- readxl::read_xlsx(path_to_K10_data_chr,
#                                        range = .x)
# tb <- tb %>%
#   dplyr::mutate_at(dplyr::vars(dplyr::starts_with('Scen')), .funs = list(RR = ~(1+(.-Baseline)/Baseline))) %>%
#   dplyr::mutate(week_starting_dtm = purrr::map_dbl(t,
#                                                    ~ start_date_dtm + lubridate::weeks(.x)))
# attributes(tb$week_starting_dtm) <- attributes(start_date_dtm)
# tb             
# }) %>%
#     stats::setNames(names(range_ls))
# 
# }
# make_bgd_RR_lup <- function(pa_x_params_ls,
#                                dates_idx_dbl_vec, # Named
#                                dates_nms_chr_vec,
#                                RR_tb,
#                                prev_data_dbl_vec){
# 
#   purrr::reduce(1:length(dates_idx_dbl_vec),
#                 .init = tibble::tibble(age_dbl = pa_x_params_ls$age_lower:pa_x_params_ls$age_upper),
#                 ~ {
#                   row_idx_dbl = .y
#                   dplyr::mutate(.x,!!rlang::sym(dates_nms_chr_vec[.y]) := purrr::map_dbl(age_dbl,
#                                                                                          
#                                                               ~ {
#                                                                 ifelse(.x<18, # Change to switch or lookup to cover all posible age ranges
#                                                                        1+(RR_tb %>%
#   dplyr::slice(row_idx_dbl) %>% dplyr::pull(Baseline)-prev_data_dbl_vec[1])/prev_data_dbl_vec[1],
#                                                                1+(RR_tb %>%
#   dplyr::slice(row_idx_dbl) %>% dplyr::pull(Baseline)-prev_data_dbl_vec[2])/prev_data_dbl_vec[2]    )
#                                                            
#                                                               }
#                                                                    ))
#                 })
# }
# update_results_ls <- function(pa_x_params_ls_path_chr,
#                               youth_distress_tb,
#                               epi_data_dtm_ls){
#   pa_x_params_ls <- readRDS(pa_x_params_ls_path_chr)
#   prev_params_dbl_vec <- purrr::map_dbl(epi_data_dtm_ls,
#                                         ~ which.min(abs(youth_distress_tb$week_starting_dtm-.x)))
# prev_data_dbl_vec <- youth_distress_tb %>% 
#   dplyr::slice(prev_params_dbl_vec) %>%
#   dplyr::pull(Baseline)
# ti_col_chr_vec <- names(pa_x_params_ls$sim_results_ls[[1]])[names(pa_x_params_ls$sim_results_ls[[1]]) %>% startsWith("ti_")] %>% stringr::str_sub(end=-6) %>% unique()
# dates_nms_chr_vec <- c("t0_RR",
#                        #ti_col_chr_vec, paste(_RR) and ADD BACK IN WHEN PREVALENCE CALCULATED FOR i TIME POINTS
#                       "tx_RR")
# int_dtm_vec <- paste0(ti_col_chr_vec %>% stringr::str_sub(start=4, end=7),
#        "-",
#        ti_col_chr_vec %>% stringr::str_sub(start=8, end=9),
#        "-",
#        ti_col_chr_vec %>% stringr::str_sub(start=10, end=11)) %>%
#   lubridate::ymd(tz = "Australia/Melbourne")
# dates_idx_dbl_vec <- purrr::map_dbl(c(pa_x_params_ls$sim_data_r4@model_start_date,
#                                       #int_dtm_vec, ADD BACK IN WHEN PREVALENCE CALCULATED FOR i TIME POINTS
#                                       pa_x_params_ls$sim_data_r4@model_end_date),
#                                     ~ which.min(abs(youth_distress_tb$week_starting_dtm-.x)))
# ## Add Interval Times
# RR_tb <- youth_distress_tb %>% dplyr::slice(dates_idx_dbl_vec)
# base_case_syd_RR_lup <- make_bgd_RR_lup(pa_x_params_ls = pa_x_params_ls,
#                                            dates_idx_dbl_vec = dates_idx_dbl_vec,
#                                            dates_nms_chr_vec = dates_nms_chr_vec,
#                                            RR_tb = RR_tb,
#                                            prev_data_dbl_vec = prev_data_dbl_vec)
# alt_results_ls <- pa_x_params_ls$sim_results_ls %>%
#   purrr::map(~ {
#     .x %>%
#       add_shock_RR_tb(RR_tb = RR_tb,
#                       starts_with_chr_vec = c("t0_prev","tx_prev")) %>%
#     add_alt_model_RR_tb(col_pfx_chr = "t0_prev",
#                           time_RR_chr = "t0_RR",
#                           RR_lup = base_case_syd_RR_lup)  %>%
#           add_alt_model_RR_tb(col_pfx_chr = "tx_prev",
#                           time_RR_chr = "tx_RR",
#                           RR_lup = base_case_syd_RR_lup) %>%
#             add_shock_RR_tb(RR_tb = RR_tb,
#                       starts_with_chr_vec = c("SYD_BC_t0_prev","SYD_BC_tx_prev"))
# 
#                }
# )
# }
# range_ls <- list(youth_distress_tb = "L3:U734",
#                  all_distress_tb = "A3:J734")
# distress_tbs_ls <- import_model_output_tb(path_to_K10_data_chr = path_to_K10_data_chr,
#                                           range_ls = range_ls,
#                                           start_date_dtm = start_date_dtm)
# scenarios_tb <- readxl::read_excel(path_to_K10_data_chr,
#                                    range = "W3:X9",
#                                    col_names = F) %>%
#   dplyr::rename(Scenario = ...1,
#                 Description = ...2)
```


```{r echo=F, warning=F, message=F, eval=T}
## MAKE FN
# epi_data_dtm_ls <- list(age_12_17 = lubridate::ymd_hms("2014-01-01 00:00:00", 
#                                      tz = "Australia/Melbourne"),
#                         age_18_25 = lubridate::ymd_hms("2011-01-01 00:00:00", # 2007 not available
#                                      tz = "Australia/Melbourne"))
# alt_results_ls <- update_results_ls(pa_x_params_ls_path_chr = pa_x_params_ls_path_chr,
#                                         youth_distress_tb = distress_tbs_ls$youth_distress_tb,
#                                         epi_data_dtm_ls = epi_data_dtm_ls)
```

