---
params:
  add_title_lgl: !r F
  age_lower: 16
  age_upper: 25
  authorship_1_chr: ""
  authorship_1_chr: ""
  data_pckg_chr: springtides
  disorder_chr: !r NA_character_
  gdist_dbl: !r NA_real_
  gdist_ttime_chr: !r NA_character_
  input_ls_path_chr: !r NA_character_
  meso2_bound_yr: !r NA_real_
  meso2_chr: !r NA_character_
  meso2_name_chr: !r NA_character_
  meso2_type_chr: POA
  micro_chr_vec: !r NA_character_
  model_end_date: !r Sys.Date()
  model_start_date: !r springtides::aus_pa_r4@temporal_min #+ lubridate::years(2)
  n_its_int: !r NA_real_
  pa_r4_chr: aus_pa_r4
  pa_type_chr: !r NA_character_
  pdf_output_lgl: !r F
  r_data_dir_chr: "data"
  rendered_by_shiny_lgl: !r F
  sim_data_r4_path_chr: !r NA_character_
  sim_results_ls_path_chr: !r NA_character_
  stat_chr: Prevalence - Annual
  title_chr: Springtides report
  ttime_dbl: !r NA_real_
  uncertainty_1_int: 0.025
  uncertainty_2_int: 0.975
  user_name_chr: !r NA_character_
title: "`r params$title_chr`"
author: 
 -  "`r params$authorship_1_chr`"
 - "`r params$authorship_2_chr`"
date: "`r format.Date(Sys.Date(),'%B %d, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document:
    fig_caption: yes
header-includes: 
  - \usepackage{booktabs} 
  - \usepackage{longtable} 
  - \usepackage{array} 
  - \usepackage{multirow} 
  - \usepackage{wrapfig} 
  - \usepackage{float}
  - \usepackage{colortbl} 
  - \usepackage{pdflscape} 
  - \usepackage{tabu} 
  - \usepackage{threeparttable} 
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem} 
  - \usepackage{makecell} 
  - \usepackage{xcolor}
---

```{r echo=F, warning=F, message=F, eval=T}
library(magrittr)
library(kableExtra)
output_params_ls <- springtides::make_output_params_ls(input_params_ls = params)
```

# Purpose
This brief report displays the input parameter values used in the function call to create this report. Key structural features of this report such as the document format, document title, author list and layout are also determined by the inputs to the function that rendered this report.

## Inputs
The inputs that were used to generated this report are a combination of default values contained in the YAML tags at the start of a template RMD document and any values specified in a list object passed to the "params" argument in a call to the render function from the rmarkdown package. The YAML tags contain the default values, but these defaults can be overwritten in the function call.

The input parameter values are contained in an object called "params" and are listed here:

```{r eval=T}
params
```

