---
params:
  add_title_lgl: !r F
  age_lower: 16
  age_upper: 25
  authorship_1_chr: !r NA_character_
  authorship_2_chr: !r NA_character_
  data_pckg_chr: springtides
  disorder_chr: Any_Affective_Disorder
  gdist_dbl: !r NA_real_
  gdist_ttime_chr: !r NA_character_
  input_ls_path_chr: "C:/Users/mahamilton/Desktop/Readyforwhatsnext/Data/Project/input_ls_4.rds"
  meso2_bound_yr: 2011
  meso2_chr: "0800"
  meso2_name_chr: "0800 Postal Area"
  meso2_type_chr: POA
  micro_chr_vec: !r NA_character_
  model_end_date: !r Sys.Date()
  model_start_date: !r springtides::aus_pa_r4@temporal_min #+ lubridate::years(2)
  n_its_int: 10
  pa_r4_chr: aus_pa_r4
  pa_type_chr: HSS
  pdf_output_lgl: !r F
  r_data_dir_chr: "C:/Users/mahamilton/Desktop/Readyforwhatsnext/Data/R_Format"
  rendered_by_shiny_lgl: !r F
  sim_data_r4_path_chr: "C:/Users/mahamilton/Desktop/Readyforwhatsnext/Data/Project/sim_data_r4_4.rds"
  sim_results_ls_path_chr: "C:/Users/mahamilton/Desktop/Readyforwhatsnext/Data/Project/sim_results_ls_4.rds"
  stat_chr: Prevalence - Annual
  title_chr: Springtides report
  ttime_dbl: !r NA_real_
  uncertainty_1_int: 0.025
  uncertainty_2_int: 0.975
  user_name_chr: Anonymous user
title: "`r params$title_chr`"
author: 
 - "Report generated by the Orygen Springtides App" 
 - "Input parameters selected by `r params$user_name_chr`"
date: "`r format.Date(Sys.Date(),'%B %d, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document:
    fig_caption: yes
header-includes: 
  - \usepackage{booktabs} 
  - \usepackage{longtable} 
  - \usepackage{array} 
  - \usepackage{multirow} 
  - \usepackage{wrapfig} 
  - \usepackage{float}
  - \usepackage{colortbl} 
  - \usepackage{pdflscape} 
  - \usepackage{tabu} 
  - \usepackage{threeparttable} 
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem} 
  - \usepackage{makecell} 
  - \usepackage{xcolor}
---

```{r echo=F, warning=F, message=F, eval=T}
library(magrittr)
library(kableExtra)
output_params_ls <- springtides::make_output_params_ls(input_params_ls = params)
```

# Purpose
This brief report displays the input parameter values used in the function call to create this report. Key structural features of this report such as the document format, document title, author list and layout are also determined by the inputs to the function that rendered this report.

## Inputs
The inputs that were used to generated this report are a combination of default values contained in the YAML tags at the start of a template RMD document and any values specified in a list object passed to the "params" argument in a call to the render function from the rmarkdown package. The YAML tags contain the default values, but these defaults can be overwritten in the function call.

The input parameter values are contained in an object called "params" and are listed here:

```{r eval=T}
params
```

